---
title: "R_programming_01"
author: "Jorge Raze"
date: "9/4/2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Programming

This is the R programming course, we'll try to focus in common tasks performed by a data scientist.

## What is R?

R is a dialect of S.

S is a language that was developed by John Chambers and others at the old Bell Telephone Laboratories, originally part of AT&T Corp. S was initiated in 1976 as an internal statistical analysis environment, originally implemented as Fortran libraries. Early versiones of the language did not even contain functions for statistical modeling.

In 1988 the system was rewritten in C and began to resemble the system that we have today (this was Version 3 of the language). The book *Statistical Models in S* by Chambers and Hastie (the white book) documents the statistical analysis functionality.Version 4 of the S language was released in 1988 and is the version that we use today. The book *Programming with Data* by john Chambers (the green book) documents this version of the language.

## Back to R

The R language came to use quite a bit after S had been deeloped. One key limitation of the S language was that it was only available in a commercial package, S-PLUS. In 1991, R was created by Ross Ihaka and Robert Gentleman in the Department of Statistics at the University of Auckland. In 1993 the first announcment of R was made to the public. Ross's and Robert's experience developing R is documented in a 1996 paper in the *Journal of Computational and Graphical Statistics*

> Ross Ihaka and Robert Gentleman. R: A language for data analysis and grapics. Jorual of Computational and Graphical Statistics, 5(3):299-314,1996

## Slide with Plot

```{r pressure}
plot(pressure)
```

